### 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
first citation ;)

  \section*{Exercise 1 - \textsl{}}

@@

>>>>

  \section*{Exercise 1 - \textsl{Smith Waterman today}}
	  The 30 years old Smith-Waterman (SW) algorithm is one of the fundamental algorithms in bioinformatics. This algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence. But the dynamic programmed algorithm has to face the problem of complexity of $O(n\times m)$. This complexity is getting a problem when starting to compare large sequences or even whole genomes.
	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm. \cite{blast}

@@

\begin{thebibliography}{widestlabel}
	\bibitem[Li, H., Homer, N.]{blast} 	
	Li, H., Homer, N. (2010). A survey of sequence alignment algorithms for next-generation sequencing. Briefings in Bioinformatics, 11(5), 473–483. http://doi.org/10.1093/bib/bbq015
\end{thebibliography}
